\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.65in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{fontawesome}

\pagestyle{empty}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\LARGE \textbf{Amaury Bilocq}}\\
    \textit{PhD Candidate | Aerospace \& Industrial Engineer | Numerical Methods \& Compressible Turbulence}\\
    Liège, Belgium \quad \faEnvelope\ \href{mailto:amaury.bilocq@gmail.com}{amaury.bilocq@gmail.com} \quad
    \faGithub\ \href{https://gitlab.uliege.be}{gitlab.com/Amaury.Bilocq} \quad
    \faGlobe\ \href{https://orbi.uliege.be/profile?uid=p216754}{orbi.uliege.be/myorbi}
\end{center}

\section*{Professional Summary}
Aerospace engineer with expertise in compressible aerodynamics, turbulence modeling, and numerical methods. Experienced in both low- and high-fidelity CFD, turbomachinery, and multidisciplinary collaboration. Passionate about automation, coding, and solving complex problem.

\section*{Education}
\textbf{PhD in Aerospace Engineering} \hfill \textit{University of Liège, Ongoing since 2020}\\
\textbf{M.Sc. Aerospace Engineering} \hfill \textit{University of Liège, 2020 (Distinction)}\\
\textbf{M.Sc. Industrial Engineering} \hfill \textit{Henallux-Pierrard, 2018 (Great Distinction)}

\section*{Experience}
\textbf{PhD Candidate, Design of turbomachines} \hfill \textit{University of Liège, 2020–Present} \\
Thesis supervisors: Prof. Koen Hillewaert \& Prof. Vincent Terrapon

Numerical research on high-speed turbulent flows and shock capturing methods for aerospace applications.
\begin{itemize}[leftmargin=1.5em]
  \item Developed from scratch a massively parallel high-order discontinuous Galerkin solver (C++/Python).
  \item Investigated shock-capturing strategies for accurately resolving compressible turbulence in high-speed flows.
  \item Implemented advanced co-processing tools for statistical analysis of large simulation data.
  \item Contributed to DevOps workflows with GitLab CI/CD and Docker for solver management and testing.
  \item Supervised master's thesis students in the field of numerical methods.
\end{itemize}

\textbf{Teaching Assistant (CFD \& Flow in turbomachines)} \hfill \textit{University of Liège, 2021–2023}

\begin{itemize}[leftmargin=1.5em]
  \item Computational Fluid Dynamics: Prepared, supervised, and corrected exams; developed and delivered practical sessions on numerical methods and turbulence modeling.
  \item Flow in Turbomachines: Provided simulation data for student projects, focusing on secondary flows around 3D rotor and stator blades in design and off-design conditions. Conducted tutorial sessions on ParaView for post-processing and flow visualization.
\end{itemize}

\textbf{Internship, Aircraft Design} \hfill \textit{University of Liège, Feb–Aug 2020}
\begin{itemize}[leftmargin=1.5em]
    \item Developed a low-fidelity model for preliminary aircraft design.
    \item Integrated a viscous–inviscid interaction model into an existing full potential solver to enhance aerodynamic performance predictions.
\end{itemize}

\textbf{Internship, Satellite Avionics Production} \hfill \textit{LuxSpace, Feb–June 2018}

\begin{itemize}[leftmargin=1.5em]
  \item Designed a production cell for microsatellite avionics using Lean 3P methodology.
  \item Integrated Industry 4.0 principles into early-stage design workflows.
\end{itemize}

\textbf{Internship, Mechanical Design} \hfill \textit{Jindal Films, Sep–Nov 2015}

\begin{itemize}[leftmargin=1.5em]
  \item Translated 2D mechanical drawings of a cutting blade station for plastic film production into functional 3D CAD assemblies using Inventor (AutoCAD).
  \item Collaborated with the machine shop to produce and install the station.
\end{itemize}

\begin{multicols}{2}

\section*{Technical Skills}
\textbf{Programming:} \texttt{Python}, \texttt{C/C++}, \texttt{MATLAB/Simulink}, \texttt{Git}  \\
\textbf{CFD Tools:} \texttt{OpenFOAM}, \texttt{SU2}, \texttt{GMSH}, \texttt{ParaView} \\
\textbf{CAD/CAE:} \texttt{Siemens NX}, \texttt{AutoCAD}, \texttt{Fusion 360} \\
\textbf{Automation:} \texttt{TIA Portal (PLC)}\\
\textbf{Operating Systems:} \texttt{Linux}, \texttt{Windows}, \texttt{macOS} \\

\columnbreak
\section*{Languages}
French (Native) \\ English (Full Professional) \\ German (Beginner)

\end{multicols}

\end{document}
